Space Matters: extending sensitivity analysis to initial spatial conditions in geosimulation models

### 2019-08-13 Response_to_Reviewers.tex

   %\comment[JR]{most of this empirical literature was added because of one CEUS reviewer, no ?}\comment[MLT]{If we want to keep this part to please everyone (like our former reviewer), we could explicitly mention that we model the growth of a city (in terms of population density) which is the results of a bunch of dynamics ... and not the dynamics themselves?}
  %\comment[FLN]{ qui montre que la démarche méta est ici appliquée à un domaine empirique qu'il aide à explorer mais d'autres domaines peuvent s'emparer de la démarche méta.}

   % show disagreement with omitting empirical/geographical but demonstrate helps understand geographical question but the is generic and valuable for it.

\medskip

  \item \textit{The problem, from a geographical point of view, is that the paper switches between “geographical” and “spatial” without making any differentiation. In so doing, the author(s) runs immediately into the problem of adequate definitions. In paragraph 1.2 the definition of geographical systems as “social agents interacting with one another, within a limited portion of space” is misleading. First, it is a tautology (geographical systems in space); secondly, geographical cannot be described with social agents, because geographical systems are composed of spatial units, their relations, and a spatially defined system border. Social systems, in turn, might be described with humans as elements, their relations, and again a socially defined system border. Moreover, with respect to sociological system theory (Luhmann 1993), space does not add any knowledge to the nature of social systems. This approach can be (and I would add: has to be) criticised, however, not by interming! ling fuzzily the social with the geographical, as happened with this definition.} 
  %\item \comment[JR]{by spatial we indeed mean some kind of spatial container for agents right ? which is far from geographical in the sense he puts it indeed}\comment[MLT]{use sociospatial system instead? The term is broadly used in the literature to describe the interdependence between social phenomena and their spatial environment. We could also quote \hyperlink{https://journals.sagepub.com/doi/abs/10.1068/d9107}{Jessop et al. 2008}}

### 2019-08-14 Response_to_Reviewers.tex

 \medskip

  %\item reprendre tout le papier pour éliminer les termes indéfinis "space", "pattern" etc. + en conclu mentionner que ça s'applique aux automates cellulaires (sans agents) et aux modèles écologiques (agents-arbres).
  %\item in conclusion, we need to clarify the answer to the question "do geometric structure influence sociospatial systems dynamics" by saying it depends on the model. ≠ black\&white and we can demonstrate it. The nature of social systems is a given (in the model mu, which is not the contribution of this paper) and we explore the consequence of geometric structures on the spatial expression of social systems.

  \item \textit{Then, in paragraph 1.3, the complexity of systems with respect to segregation is also problematically described.} \ldots
  % Emergent behaviour that may lead to segregation is first and foremost a social process, taking social interactions at the local scale (income, housing costs, etc.) and/or at the macro scale (laws, rules, economic system, cultural attitudes, etc.) into account. These interactions can then be associated with the material and relational dimension of geographical spaces. The question remains: what is the role of geographical systems? In this respect, the paper offers some relevant clues such as the MAUP problem or the “uncertain geographic context problem”.

  $\rightarrow$ see comment A. As for the role of geometric structures in the production of segregation, Banos (2012) has shown that with the same Schelling mechanisms and the same parameter values but different network structures of neighbourhoods (scale-free, regular, etC.) the segregation observed at the end of simulation varied significantly between network structures. This is the kind of approach we systematise here, although with a spatial grid instead of network structures.

@@

  $\rightarrow$ This point was not explicit enough and we revised the presentation of our approach (which is generic and not empirical) in introduction (especially fig. 1), as already stated in comment B.3 above. We thank reviewer 2 for highlighting this limitation.
  % \item \comment[JR]{this is a relevant remark but far beyond the scope of the paper, as an extension of what we did but with perturbation of real datasets / sensitivity to noise - Julien wanted to begin working on that actually and it should be integrated into spatialdata at some point - we also are supposed to implement such a perturbator to test the 4city model}

  \medskip

  \item \textit{Furthermore, there are now examples of spatial models that go beyond administrative neighborhoods and overimposed spatial boundaries, i.e., egohoods (e.g., https://onlinelibrary.wiley.com/doi/abs/10.1111/1745-9125.12006), which could be interesting to see implemented in ABM.}

  $\rightarrow$ We added a paragraph on the limits of our density grid approach in discussion, in which we mention the possibility to use egohoods to better measure segregation. Indeed, at present, the use of a grid of varying density means that in dense areas, agents have many neighbours and thus a higher probability of mixing, which affects segregation measurement. With egohoods, each agents would have the same number of neighbours taken into account for the calcultation, but their spatial scope would vary (for some agents, it would be for example 100 neighbours from the same cell whereas for others, it would be the nearest 100 neighbours taken from 25 surrounding cells).

### 2019-08-14 paper.tex
.
Update on Overleaf.

\author[6]{Florent Le N{\' e}chet}
\affil[6]{Universit{\'e} Paris-Est, Laboratoire Ville Mobilit{\'e} Transport, Marne-la-Vallée, France}

@@

\begin{abstract}
Although simulation models of socio-spatial systems in general and agent-based models in particular represent a fantastic opportunity to explore socio-spatial behaviours and to test a variety of scenarios for public policy, the validity of generative models is uncertain unless their results are proven robust and representative of 'real-world' conditions. Sensitivity analysis usually includes the analysis of the effect of stochasticity on the variability of results, as well as the effects of small parameter changes. However, initial spatial conditions are usually not modified systematically in socio-spatial models, thus leaving unexplored the effect of initial spatial arrangements on the interactions of agents with one another as well as with their environment. In this paper, we present a method to assess the effect of some initial spatial conditions on simulation models, using a systematic geometric structures generator in order to create density grids with which socio-spatial simulation models are initialised. We show, with the example of two classical agent-based models (Schelling's models of segregation and Sugarscape's model of unequal societies) and a straightforward open-source work-flow using high performance computing, that the effect of initial spatial arrangements is significant on the two models. We wish to illustrate the potential interest of adding spatial sensitivity analysis during the exploration of models for both modellers and thematic specialists.%Furthermore, this effect is sometimes larger than the effect of parameters' value change.%Comment FL : j'ai supprimé cette dernière phrase qui ne me semblait pas essentielle et rajouté à la place une phrase d'ouverture de Marion.
\end{abstract}

@@

Computer simulation has been recognised and is increasingly used by geographers as an efficient tool to explore geographical processes, hypotheses and predictive scenarios within virtual laboratories \citep{batty1971modelling, batty2007model, carley1999generating, Quesneletal2009}. It has been identified as an emerging field and coined under the term geosimulation by \cite{benenson2004geosimulation}. Simulation also appears as a way to overcome the difficult analytic resolution of many socio-spatial models which were developed in the past, as well as to explore the possible (alternative) trajectories of path-dependent social and ecological systems. The specificity of geographical models compared to other social science models is that space and spatial interactions are given a prime role, geographers being driven by an explicit interest in studying the way "space" in broad sense influences the outcomes of social processes modelled. We think that simulation approaches are uniquely positioned to represent the complexity of socio-spatial interactions, provided that models include relevant spatial descriptions and behavioural rules which take space into account, and provided that the model evaluation includes a sensitivity analysis of the model outputs to the way space is represented. Unfortunately, the first condition is not always met, and the second is seldom even mentioned. This paper aims to fill a methodological and conceptual gap, which is a systematic testing of the sensitivity of a model's outcomes to its initial spatial conditions. \comment[FL]{il faut ici citer des approches du même type}. To demonstrate the genericity of our approach, we develop two applications with classic simulation models commonly used as case studies for comparing and aligning simulation models \citep{Axtelletal1996, wilensky2007making}: \citet{schelling1971dynamic}'s model of segregation and \citet{EpsteinAxtell1996}'s Sugarscape model.\\

@@

Finally, although this may seem obvious, cities are not regular grids, and the distribution of density (of jobs, residents, buildings, etc.) is far from isotropic, even in sprawled cities. On the contrary, there is a significant diversity in the way people, activities and structures are distributed in cities. In Europe for example, \citet{LeNechet2015} quantifies and classifies six broad types of residential density distributions. However, most socio-spatial models, especially cellular automata, still represent cities as uniform grids of isotropic density. Even in applied cases when GIS geometries of a particular city are used, the spatial distribution of agents tend to be approximated by a constant density \citep{arribas2014diverse}, although previous research shows that it is computationally and methodologically feasible to use accurate locations in a simple model such as Schelling's \citep{benenson2002entity}. The isotropic simplification is potentially harmful to the representation of urban processes because density and accessibility have environmental, economic and social consequences. Additionally, we expect the initial spatial distribution of agents to influence simulation results in the long run \citep{Castellanoetal2009}, because the agents' rule of action itself may depend on the spatial structure of the environment. For example, households can have different preferences with respect to the built-environment they might want to live in \citep{SpielmanHarrison2014}, or agents moving around will sense a different set of objects within the same fixed radius depending on the topology \citep{Banos2012} and distribution of density of the sensed environment \citep{LauriJaggi2003, FossettDietrich2009}. The way modellers represent initial space is therefore a central element of socio-spatial simulation models. However, this step is rarely explicit. A meaningful way of representing initial space might be to consider, not necessarily the peculiarities of every city, but at least their broad density structures so as to estimate the variability of the model behaviour to different plausible spatial arrangements.

@@

In order to generate density grids which correspond to empirical density distributions, we select among the generated grids using an objective function which matches the point cloud of 110 metropolitan areas in Europe described by four dimensions of spatial structure: their concentration index, hierarchy index, centrality index and homogeneity index (cf. \cite{LeNechet2015}). These four dimensions were chosen as complementary descriptors of spatial organisation at urban or metropolitain level - see also \cite{tsai2005quantifying} and \cite{schwarz2010urban}. They account for : , the extend to which population is clustered in a central city, at macro scale (centrality) and micro scale (concentration), the extent to which density grid values are similar or contrasted, regardless of location, at macro scale (hierarchy) and micro scale (homogeneity)\comment[FL]{check with Juste quels indicateurs ont été utlisés}. These morphological dimensions are in practice captured using the rank-size slope to capture hierarchy, the average distance between individuals to capture concentration, distribution entropy to capture homogeneity, and Moran spatial autocorrelation index to measure centrality.

We sample the generator parameter space using a Latin Hypercube Sampling, which is a convenient technique to have a scatter with low discrepancy in high dimensions. We sample 2000 points in the 4-dimensional space of parameters {$\alpha$, $\beta$, $n_d$, $N$}. It yields a subset of 170 grids matching empirical densities, which constituted our set of different initial spatial conditions. These are further clustered into three classes of morphology (figure \ref{fig:densityTypes}): compact (e.g. Vienna), polycentric (Liege) and discontinuous (Augsburg). This clustering allows to evaluate the non-trivial effects of a meaningful urban form on simulation results. We select 15 grids of each type to work with in the computation of sensitivity analysis of an intra-urban model (cf. section \ref{sec:qualResults}).
\comment[FL]{à discuter}
The spatial generator and its resulting grids are relevant to the case study models we have picked (Schelling and Sugarscape) because it produces density grids at a ``metropolitan scale'', which is the scale at which both model were initially intended to be. In the case of Schelling's segregation model for example, this scale is the one at which most empirical segregation indexes are computed and compared to the model outputs. In the case of Sugarscape, it corresponds to the whole city if the model is a metaphor for city resources \citep{batty2005agents}, or to a generic landscape where a resource is grown otherwise. In both cases, our point is that there exist many different patterns of density distribution in resource location and urban density and that acknowledging this diversity might leads to a variation in the model outputs. Furthermore, in urban models, we argue that the hypothesis of isotropic density is potentially the most unrealistic one, although unfortunately the most common one in Schelling implementations.

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!t]
\centering
	%\includegraphics[width=0.9\textwidth]{figuresraw/GridPresentation.png}
	\includegraphics[width=0.9\textwidth]{figures/Fig3.png}
 \caption{Correspondence between European urban density structures and grids produced with the spatial generator.} 
\label{fig:densityTypes}
\end{figure} %
%%%%%%%%%%%%%%%%%%%%%%
\comment[FL]{à discuter, rappeler sens des paramètres alpha, beta, etc. ; pourquoi appeler cela des "meta paramètres"? maintenant on appele cela des gamma parametres?}

@@

@@

Although the applications we present here are limited by the simplicity of the models, we think that the method could (and should) be applied to larger models including domain mechanisms and more empirical initialisation data, for example synthetic populations. The sensitivity analysis to initial spatial conditions could then be either a replication on the spatial allocation of the synthetic population, or a series of spatial permutations of the empirical spatial inputs.
We want to foster this extension of our work by releasing the density grids also generated, as well as the generating work-flow and the model implementation. They are available on the open repository of the project at \url{https://github.com/AnonymousAuthor2/SpaceMatters}. Future work could be done to compare these or generate grids with a larger morphological span, covering other typical urban forms that can be found in the world.

@@

This relates to relations between empirical, conceptual and modeling dimensions of quantitative research in social sciences, as coined by \cite{livet2010ontology}. In our case, a contribution in the modeling domain aiming at extracting further knowledge on model behavior (sensitivity to geometrical context), naturally leads to questioning theoretical concepts and empirical definition on which the model was based, such as for example the meaning of neighborhood.
% to inform the interactions between empirics, concepts and models as discussed by Livet et al., 2010, we added a paragraph in conclusion, discussing how our approach allows to go back to questioning empirical cases from the model and questioning our concepts (for example how ’neighbourhood’ is modelled since Schelling compared to the meaning of neighbourhood in empirical/theoretical social sciences)

\section{Conclusion}

After reviewing the extensive literature on spatial biases in statistical and simulation models, we presented a method to analyse the sensitivity of a simulation's results to the initial spatial configuration. We did so by implementing a spatial generator whose output is used as input for the simulation model. We applied this approach to two textbook ABMs: Schelling and Sugarscape. With the Schelling experiment, we found that the different urban morphologies impact the interaction patterns, and that polycentric and discontinuous cities appear systematically more segregated than compact cities in terms of dissimilarity and entropy index. With Sugarscape, we show that the model is more sensitive to space than to its other parameters in the reference Netlogo implementation, both qualitatively and quantitatively: the amplitude of variations across density grids is larger than the amplitude in each phase diagram, and the behaviour of the phase diagram is qualitatively different in different regions of the morphological space. We think that this method has the potential to increase the arsenal of evaluation of socio-spatial models, in order to assess the sensitivity of models to their initial spatial conditions but also to learn about the impact of the urban form on social mechanisms.

>>>>

\author[6]{Florent Le N{\' e}chet}
\affil[6]{Universit{\'e} Paris-Est, Laboratoire Ville Mobilit{\'e} Transport, UMR-T 9403, Université Paris-Est Marne-la-Vallée, France}

@@

\begin{abstract}
\comment[FL]{le titre de l'article ce serait presque "geometry" matters? non?}
Although simulation models of socio-spatial systems in general and agent-based models in particular represent a fantastic opportunity to explore socio-spatial behaviours and to test a variety of scenarios for public policy, the validity of generative models is uncertain unless their results are proven robust and representative of 'real-world' conditions. Sensitivity analysis usually includes the analysis of the effect of stochasticity on the variability of results, as well as the effects of small parameter changes. However, initial spatial conditions are usually not modified systematically in socio-spatial models, thus leaving unexplored the effect of initial spatial arrangements on the interactions of agents with one another as well as with their environment. In this paper, we present a method to assess the effect of some initial spatial conditions on simulation models, using a systematic geometric structures generator in order to create density grids with which socio-spatial simulation models are initialised. We show, with the example of two classical agent-based models (Schelling's models of segregation and Sugarscape's model of unequal societies) and a straightforward open-source work-flow using high performance computing, that the effect of initial spatial arrangements is significant on the two models. We wish to illustrate the potential interest of adding spatial sensitivity analysis during the exploration of models for both modellers and thematic specialists.%Furthermore, this effect is sometimes larger than the effect of parameters' value change.%Comment FL : j'ai supprimé cette dernière phrase qui ne me semblait pas essentielle et rajouté à la place une phrase d'ouverture de Marion.
\end{abstract}

@@

Computer simulation has been recognised and is increasingly used by geographers as an efficient tool to explore geographical processes, hypotheses and predictive scenarios within virtual laboratories \citep{batty1971modelling, batty2007model, carley1999generating, Quesneletal2009}. It has been identified as an emerging field and coined under the term geosimulation by \cite{benenson2004geosimulation}. Simulation also appears as a way to overcome the difficult analytic resolution of many socio-spatial models which were developed in the past, as well as to explore the possible (alternative) trajectories of path-dependent social and ecological systems. The specificity of geographical models compared to other social science models is that space and spatial interactions are given a prime role, geographers being driven by an explicit interest in studying the way "space" in broad sense, and more specifically geometry or topology of space influences the outcomes of social processes modelled. We think that simulation approaches are uniquely positioned to represent the complexity of socio-spatial interactions, provided that models include relevant spatial descriptions and behavioural rules which take spatial proximity into account, and provided that the model evaluation includes a sensitivity analysis of the model outputs to the way space is represented. Unfortunately, the first condition is not always met, and the second is seldom even mentioned. Various contribution have been made on ad hoc models to test for the influence of geometry on simulation outputs \citep{lilburne2009sensitivity, sun2007traffic}, but without providing a generic framework fitted for most agent-based models. This paper aims to fill a methodological and conceptual gap, which is a systematic testing of the sensitivity of a model's outcomes to its initial spatial conditions. To demonstrate the genericity of our approach, we develop two applications with classic simulation models commonly used as case studies for comparing and aligning simulation models \citep{Axtelletal1996, wilensky2007making}: \citet{schelling1971dynamic}'s model of segregation and \citet{EpsteinAxtell1996}'s Sugarscape model.\\

@@

Finally, although this may seem obvious, cities are not regular grids, and the distribution of density (of jobs, residents, buildings, etc.) is far from isotropic, even in sprawled cities. On the contrary, there is a significant diversity in the way people, activities and structures are distributed in cities. In Europe for example, \citet{LeNechet2015} quantifies and classifies six broad types of residential density distributions. However, most socio-spatial models, especially cellular automata, still represent cities as uniform grids of isotropic density. Even in applied cases when GIS geometries of a particular city are used, the spatial distribution of agents tend to be approximated by a constant density \citep{arribas2014diverse}, although previous research shows that it is computationally and methodologically feasible to use accurate locations in a simple model such as Schelling's \citep{benenson2002entity}. The isotropic simplification is potentially harmful to the representation of urban processes because density and accessibility have environmental, economic and social consequences. Additionally, we expect the initial spatial distribution of agents to influence simulation results in the long run \citep{Castellanoetal2009}, because the agents' rule of action itself may depend on the spatial structure of the environment. For example, households can have different preferences with respect to the built-environment they might want to live in \citep{SpielmanHarrison2014}, or agents moving around will sense a different set of objects within the same fixed radius depending on the topology \citep{Banos2012} and distribution of density of the sensed environment \citep{LauriJaggi2003, FossettDietrich2009}. The way modellers represent initial geometry of space is therefore a central element of socio-spatial simulation models. However, this step is rarely explicit. A meaningful way to address it might be to consider, not necessarily the peculiarities of every city, but at least their broad density structures so as to estimate the variability of the model behaviour to different plausible spatial arrangements.

@@

In order to generate density grids which correspond to empirical density distributions, we select among the generated grids using an objective function which matches the point cloud of 110 metropolitan areas in Europe described by four dimensions of spatial structure: their concentration index, hierarchy index, centrality index and homogeneity index (cf. \cite{LeNechet2015}). These four dimensions were chosen as complementary descriptors of spatial organisation at urban or metropolitain level - see also \cite{tsai2005quantifying} and \cite{schwarz2010urban}. They account for : the extend to which population is clustered in a central city, with two complementary indicators : Moran index (called "centrality") and distance between individuals ("concentration), the extent to which density grid values are similar or contrasted, regardless of location, with two complementary indicators : entropy of distribution ("homogeneity") and rank-size slope ("hierarchy").

We sample the $\gamma$ parameter space using a Latin Hypercube Sampling, which is a convenient technique to have a scatter with low discrepancy in high dimensions. We sample 2000 points in the 4-dimensional space of parameters {$\alpha$, $\beta$, $n_d$, $N$}. It yields a subset of 170 grids matching empirical densities, which constituted our set of different initial spatial conditions. These are further clustered into three classes of morphology (figure \ref{fig:densityTypes}): compact (e.g. Vienna), polycentric (Liege) and discontinuous (Augsburg). This clustering allows to evaluate the non-trivial effects of a meaningful urban form on simulation results. We select 15 grids of each type to work with in the computation of sensitivity analysis of an intra-urban model (cf. section \ref{sec:qualResults}).
\comment[FL]{à discuter}
The spatial generator and its resulting grids are relevant to the case study models we have picked (Schelling and Sugarscape) because it produces density grids at a ``metropolitan scale'', which is the scale at which both model were initially intended to be. In the case of Schelling's segregation model for example, this scale is the one at which most empirical segregation indexes are computed and compared to the model outputs. In the case of Sugarscape, it corresponds to the whole city if the model is a metaphor for city resources \citep{batty2005agents}, or to a generic landscape where a resource is grown otherwise. In both cases, our point is that there exist many different patterns of density distribution in resource location and urban density and that acknowledging this diversity might leads to a variation in the model outputs. Furthermore, in urban models, we argue that the hypothesis of isotropic density is potentially the most unrealistic one, although unfortunately the most common one in Schelling implementations.

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!t]
\centering
	%\includegraphics[width=0.9\textwidth]{figuresraw/GridPresentation.png}
	\includegraphics[width=0.9\textwidth]{figures/Fig3.png}
 \caption{Correspondence between European urban density structures and grids produced with the spatial generator.}
 \comment[FL]{à discuter, rappeler sens des paramètres alpha, beta, etc. ; pourquoi appeler cela des "meta paramètres"? maintenant on appele cela des gamma parametres?} \comment[JR]{+ correc nombre de chiffres significatifs}
\label{fig:densityTypes}
\end{figure} %
%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Conclusion}
\comment[FL]{je déplace cette section, remettez là à la fin si vous pensez que c'était mieux}
After reviewing the extensive literature on spatial biases in statistical and simulation models, we presented a method to analyse the sensitivity of a simulation's results to the initial spatial configuration. We did so by implementing a spatial generator whose output is used as input for the simulation model. We applied this approach to two textbook ABMs: Schelling and Sugarscape. With the Schelling experiment, we found that the different urban morphologies impact the interaction patterns, and that polycentric and discontinuous cities appear systematically more segregated than compact cities in terms of dissimilarity and entropy index. With Sugarscape, we show that the model is more sensitive to space than to its other parameters in the reference Netlogo implementation, both qualitatively and quantitatively: the amplitude of variations across density grids is larger than the amplitude in each phase diagram, and the behaviour of the phase diagram is qualitatively different in different regions of the morphological space. We think that this method has the potential to increase the arsenal of evaluation of socio-spatial models, in order to assess the sensitivity of models to their initial spatial conditions but also to learn about the impact of the urban form on social mechanisms.

@@

We wish to underline the interest of adding sensitivity analysis of the geometry of space during the exploration of models. As we have observed for simple agent-based models, uncertainties in the initial distribution of space on which agents will interact play a role on the variability in model outputs. This would certainly be even more important for more sophisticated model, with more type of agents and type of interactions, insomuch as agent-based model tend to be used in realistic, diverse settings. Therefore, we believe that for many applied problems, studying the specific variability of model outputs regarding the geometry of space would be important to assess the transferability of results in other urban settings.

This is especially important in the context of the increasing recognition of the complexity of urban space and of the role cities plays in various aspects of sustainability : modelling cities with agent-based models might become more frequent \citep{perez2016agent} and we argue it is important to account for the diversity of urban configurations when disseminating the results of any model in the planning community.

we think that the method could (and should) be applied to larger models including domain mechanisms and more empirical initialisation data, for example synthetic populations. The sensitivity analysis to initial spatial conditions could then be either a replication on the spatial allocation of the synthetic population, or a series of spatial permutations of the empirical spatial inputs.
We want to foster this extension of our work by releasing the density grids also generated, as well as the generating work-flow and the model implementation. They are available on the open repository of the project at \url{https://github.com/AnonymousAuthor2/SpaceMatters}. Future work could be done to compare these or generate grids with a larger morphological span, covering other typical urban forms that can be found in the world.

@@

This relates to relations between empirical, conceptual and modeling dimensions of quantitative research in social sciences, as coined by \cite{livet2010ontology}. In our case, a contribution in the modeling domain aiming at extracting further knowledge on model behavior (sensitivity to geometrical context), may lead to questioning theoretical concepts and empirical definition on which the model was based, such as for example the meaning of neighborhood, hence geometry of space!

% to inform the interactions between empirics, concepts and models as discussed by Livet et al., 2010, we added a paragraph in conclusion, discussing how our approach allows to go back to questioning empirical cases from the model and questioning our concepts (for example how ’neighbourhood’ is modelled since Schelling compared to the meaning of neighbourhood in empirical/theoretical social sciences)
